\section{Teamwork Description}\label{sec:team-work-description}

% This section can be skipped if the group is composed of only one person.

% Describe how you decided to work as a team and the approach you 
% have used. Describe how you planned the communication between all of you.

Our team consisted of Esben, Karsten, Tobias, and Yannick. The members of our group have worked together before, so this helped quite a lot in the beginning of the project. We were quite fast to start developing the first challenge. We divided it into smaller tasks, so we all could help build it. When it came to the other four challenges, we each came up with our own idea and began developing them individually. We still met up and talked about the problems we faced, and showed our progress. At the end of the project, we also tried each other's challenges, within our group, such that we could get feedback on them.

\subsection{Communication}

We used Messenger to set up a group for online communication. We used this to plan when and where we wanted to meet. We also used Microsoft Outlook to create calendar events for meetings and deadlines.

\subsection{Supervisor Meetings}

Everybody could not always make it to the supervisor meetings, but we made sure to always have at least one representative from our group attend them. This person would then talk and convey questions on behalf of the entire group, and write notes down to inform the other members of what happened.

\subsection{Individual Reports}

We have also each written an individual report that reflects on the project. They can be found attached to each of our submissions as \texttt{individual-report.pdf}.